Is high social class always beneficial for survival? A study of northern Sweden 1801--2013

### 2018-09-18 marginal.Rmd
fix yaml error

---
title: "Is high social class always beneficial for survival? A study of northern Sweden 1801--2013"
author: X \footnote{Corresponding author; Phone number +0000000000, email X@xcom.com}
  and Y
date: '`r Sys.Date()`'
output:
  bookdown::html_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: yes
    number_sections: yes
    toc: no
    toc_depth: 2
  bookdown::word_document2:
    toc: yes
    toc_depth: 2
citation_package: natbib
classoption: titlepage
biblio-style: apalike
documentclass: article
fontsize: 12pt
header-includes:
- \usepackage[utf8]{inputenc}
- \usepackage{graphicx}
- \usepackage{endfloat}
bibliography: mybib
abstract: "Focusing on two regions in northern Sweden 1801--2013, we challenge common
  notions of the assumed advantage in survival of belonging to a high social class.
  The issue is analysed according to gender and age group (adults and elderly) and
  in relation to the development of economic inequality. The results show that high
  social class is not always favourable for survival. Men in the elite category, particularly
  in working age, had higher mortality compared to others during a large part of the
  studied period; a male mortality class reversal appears at a surprisingly late date,
  while the social gradient among women conforms to the expected pattern. We suggest
  that health-related behaviour is decisive not only in later but earlier phases of
  the mortality transition as well. The results implicate that the association between
  social class and health is more complex than is assumed in many of the dominant
  in mortality; Cox regression; Gender differences; Inverse probability weighting;
  Mortality transition; Northern Sweden; Social inequality; 19th to 21 century "
  theories in demography and epidemiology.\\par\n\\textbf{Keywords:} Class reversal
titlepage: yes
---

>>>>

---
title: "Is high social class always beneficial for survival? A study of northern Sweden 1801--2013"
author: X \footnote{Corresponding author; Phone number +0000000000, email X@xcom.com}
  and Y
date: '`r Sys.Date()`'
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: yes
    number_sections: yes
    toc: no
    toc_depth: 2
  bookdown::html_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
  bookdown::word_document2:
    toc: yes
    toc_depth: 2
citation_package: natbib
classoption: titlepage
biblio-style: apalike
documentclass: article
fontsize: 12pt
header-includes:
- \usepackage[utf8]{inputenc}
- \usepackage{graphicx}
- \usepackage{endfloat}
- \usepackage{setspace}
bibliography: mybib
abstract: "Focusing on two regions in northern Sweden 1801--2013, we challenge common
  notions of the assumed advantage in survival of belonging to a high social class.
  The issue is analysed according to gender and age group (adults and elderly) and
  in relation to the development of economic inequality. The results show that high
  social class is not always favourable for survival. Men in the elite category, particularly
  in working age, had higher mortality compared to others during a large part of the
  studied period; a male mortality class reversal appears at a surprisingly late date,
  while the social gradient among women conforms to the expected pattern. We suggest
  that health-related behaviour is decisive not only in later but earlier phases of
  the mortality transition as well. The results implicate that the association between
  social class and health is more complex than is assumed in many of the dominant
    theories in demography and epidemiology.\\par\n\\textbf{Keywords:} Class reversal
  in mortality; Cox regression; Gender differences; Inverse probability weighting;
  Mortality transition; Northern Sweden; Social inequality; 19th to 21 century."

titlepage: yes
---

\doublespacing
